---
title: "Getting started with binomial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

# Binomial Package

The package `binomial` can be used to perform various calculations on the Binomial Distribution. The binomial distribution is a theoretical probability model used to calculate probabilities about the number of successes in a fixed number of random trials performed under identical conditions, assuming a constant probability of success on each trial. 

{insert formula}

* *n* is the number of fixed trials
* *p* is the probability of success on each trial
* *1-p* is the probability of failure on each trial
* *k* is a variable that represents the number of successes out of n trials
* (n k) is the number of combinations in which *k* successes can occur in *n* trials

# Example: Tossing a Coin 

An example of a binomial random variable is the number of heads or tails that you get when tossing a coin *n* times. In this case, *p* is 0.5. 

Say we are interested in finding the probability of getting 2 heads (k = 2) in 5 trials. 

You can use the function `bin_choose()` to calculate the number of combinations in which *k* successes can occur in *n* trials, passing in *n* and *k* as arguments. The number of combinations of getting 2 successes in 5 trials would be: 

```{r}
bin_choose(n = 5, k = 2)
```

The function `bin_probability()` calculates the probability of getting *k* successes in *n* trials with probability of success *prob*. Below is the probability of getting 2 successes in 5 trials:

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

You can create a **binomial probability distribution** by calculating this probability for all possible values for the number of successes. The output is an object of class `bindis` and `data.frame`. The data frame has `success` in the first column and `probability` in the second column.

```{r}
bin_distribution(trials = 5, prob = 0.5)
```

You can also plot a histogram of your binomial distribution using the method `plot()`:

```{r}
plot(bin_distribution(5, 0.5))
```

If you would like to see the cumulative probabilities of your distribution, you can use the function `bin_cumulative()`. The output is an object of class `bincum` and `data.frame`. THe data frame has `success` in the first column, `probability` in the second column, and `cumulative` in the third column.

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

You can graph the cumulative distribution:

```{r}
plot(bin_cumulative(trials = 5, prob = 0.5))
```

The function `bin_variable()` concisely summarizes the features of your binomial distribution. This function takes 2 arguments (`trials` and `prob`) and returns an object of class `binvar`, a list with named elements: `trials` and `prob`.

```{r}
bin_variable(trials = 10, p = 0.3)
```

You can get a full summary description of a `binvar` object by calling `summary()`. The function returns a list of class `summary.binvar` containing named elements: trials, prob, mean, variance, mode, skewness, and kurtosis.

```{r}
summary(bin_variable(trials = 10, p = 0.3))
```

# Summary Measures

The `binomial` package can also compute summary measures for a binomial distribution. These functions all take 2 arguments: `trials` and `prob`. 

The summary measures that can be computed are: 

* mean
* variance
* mode
* skewness
* kurtosis

```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

